## Investigation (i.e.) Project sheet

```{r}
#| label: setup
#| include: false
source("R/utils.R")
```

```{r}
#| echo: false
#| output: asis

tables <- data_as_gt_tables("data/investigation.csv", projects_ongoing = projects_ongoing)

for (tab in tables) {
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  "tab",
  "```"
)))
}
```

## Action (activity/study) sheet

The last updated date and release date are metadata fields more applicable to the repository where the data is deposited and is not fully the responsibility of the WP5 researcher generating the data. They have been included here for the sake of completeness. 

```{r}
#| echo: false
#| output: asis

tables <- data_as_gt_tables("data/action.csv", projects_ongoing = projects_ongoing)

for (tab in tables) {
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  "tab",
  "```"
)))
}
```

## Test Substance Sheet

```{r}
#| echo: false
#| output: asis

tables <- data_as_gt_tables("data/test_substance.csv", projects_ongoing = projects_ongoing)

for (tab in tables) {
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  "tab",
  "```"
)))
}
```

## Positive Control Sheet

```{r}
#| echo: false
#| output: asis

tables <- data_as_gt_tables("data/control_pos.csv", projects_ongoing = projects_ongoing)

for (tab in tables) {
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  "tab",
  "```"
)))
}
```

## Negative Control Sheet

```{r}
#| echo: false
#| output: asis

tables <- data_as_gt_tables("data/control_neg.csv", projects_ongoing = projects_ongoing)

for (tab in tables) {
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  "tab",
  "```"
)))
}
```

## Assay Sheet

```{r}
#| echo: false
#| output: asis

tables <- data_as_gt_tables("data/assay_sheet.csv", projects_ongoing = projects_ongoing)

for (tab in tables) {
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  "tab",
  "```"
)))
}
```

## Assay Summary Result sheet

```{r}
#| echo: false
#| output: asis

tables <- data_as_gt_tables("data/assay_summary_result.csv", projects_ongoing = projects_ongoing)

for (tab in tables) {
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  "tab",
  "```"
)))
}
```